---
title: "R Code for Evaluating the Effects of Randomness on Missing Data in Archaeological Networks"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
---

# Setup

## Load libraries

```{r}
library(tidyverse)
library(magrittr)
library(tictoc)
library(igraph)
library(ggnetwork)
library(ggthemes)
library(NetworkDistance)
library(huxtable)
```

## Custom functions

```{r}
#' Load all data by specifying one complete name or the
#' partial date file name

loadRun = function(fileName) {
  if (file.exists(stringr::str_glue('results/{fileName}'))) {
    fileName %<>% str_remove_all('run_[A-z]*_')
  }
  map(list.files('results', pattern = fileName,
                 full.names = T) %>% .[str_detect(., fileName)],
      ~
        read_csv(.x)) %>% set_names(c('assemblages',
                                      'links',
                                      'nodes',
                                      'variables'))
}

#' Convert NetLogo list format into R list
bracket2list = function(x) {
  if (str_detect(x, '[0-9]')) {
    x %>%
      str_remove_all('\\]|\\[') %>%
      str_split_fixed(' ', n = Inf) %>%
      matrix(ncol = 2, byrow = T) %>%
      as_tibble(.name_repair = "minimal") %>%
      setNames(c("tick", "tool"))
  } else {
    NA
  }
}

#' Format assemblages into a data frame structure
formatAssemblages = function(assemblages) {
  tic()
  tmp = assemblages %>%
    # remove the aggregation sites
    filter(!is.na(band)) %>%
    mutate_at(vars(band, site), as.character)
  pot = tmp %>%
    select(band, site, potAssemblage) %>%
    mutate(potAssemblage = potAssemblage %>%
             map(bracket2list)) %>%
    unnest(potAssemblage) %>%
    mutate(type = "pot") %>%
    select(band, site, tick, type, tool)
  point = tmp %>%
    select(band, site, pointAssemblage) %>%
    mutate(pointAssemblage = pointAssemblage %>%
             map(bracket2list)) %>%
    unnest(pointAssemblage) %>%
    mutate(type = "point") %>%
    select(band, site, tick, type, tool)
  print(toc()$elapsed)
  return(bind_rows(pot, point))
}

#' Create attribute network
attrNetworks = function(runResults,
                        attr = "pointAttributes",
                        group = "who") {
  links = runResults$nodes %>%
    select(who, band, camp,!!as.name(attr)) %>%
    mutate(attr = !!as.name(attr) %>% str_remove_all("\\[|\\]")) %>%
    select(-!!as.name(attr)) %>%
    separate_rows(attr, sep = " ")
  # table(links$who,links$attr)
  if (group == "camp") {
    links %<>%
      select(-who) %>%
      distinct_all()
  } else if (group == "band") {
    links %<>%
      select(-who, -camp) %>%
      distinct_all()
  }
  d =
    table(links[[group]],
          links$attr)
  n = nrow(d)
  m = matrix(nrow = n, ncol = n)
  rownames(m) = rownames(d)
  colnames(m) = rownames(d)
  for (i in 1:n) {
    for (j in 1:n) {
      r1 = which(d[i, ] > 0)
      r2 = which(d[j, ] > 0)
      m[i, j] = intersect(r1,
                          r2) %>%
        length()
    }
  }
  m
  diag(m) = 0
  m[which(m < 2)] = 0
  g = list()
  g$links = as.data.frame(m) %>%
    rownames_to_column('from') %>%
    pivot_longer(2:ncol(.), names_to = 'to', values_to = 'weight') %>%
    filter(weight > 0) %>%
    mutate(id = map2_chr(from, to,
                         ~ paste0(min(.x, .y), "_", max(.x, .y)))) %>%
    distinct(id, .keep_all = T) %>%
    select(-id)
  g$nodes = links %>%
    mutate(name = !!as.name(group)) %>%
    mutate_all(as.character) %>%
    mutate_at(vars(any_of(c(
      'who', 'name', 'camp', 'band'
    ))), list(function(x) {
      factor(x, levels = unique(x) %>% gtools::mixedsort())
    }))
  return(g)
}

#' Format Netlogo Adjacency Tables
formatNLAdjTables = function(x, p, nB = 3, cutoff = 0) {
  nms = nB:(nB * 3 + nB - 1)
  links = x %>%
    strsplit(" |\\[|\\]") %>%
    unlist %>%
    as.numeric() %>%
    .[which(!is.na(.))] %>%
    matrix(nrow = length(nms),
           ncol = length(nms),
           byrow = T) %>%
    set_colnames(nms) %>%
    set_rownames(nms) %>%
    as.data.frame() %>%
    rownames_to_column('from') %>%
    pivot_longer(all_of(nms %>% as.character),
                 names_to = "to",
                 values_to = "weight") %>%
    filter(weight > 0) %>%
    mutate(property = p,
           id = map2_chr(from, to, function(f, t) {
             sort(c(f, t)) %>%
               paste(collapse = "_")
           })) %>%
    distinct(id, .keep_all = T) %>%
    select(-id) %>%
    separate(
      col = property,
      into = c("run_number", "property"),
      sep = "_",
      extra = "drop"
    ) %>%
    slice_sample(prop = (1 - cutoff), weight_by = weight)
  nodes = tibble(camp = nms,
                 band = rep((1:nB - 1), 3) %>% sort) %>%
    mutate_all(as.character) %>%
    mutate(name = camp)
  return(list(links = links, nodes = nodes))
}

#' Calculate similarity
calcDistanceTools = function(analysis,
                              toolType = "pot",
                              group = "band",
                              cutoff = 0,
                              similarity = "WJ") {
  tmp = analysis %>%
    filter(type == toolType)
  m = table(tmp[[group]], tmp$tool) %>%
    prop.table(1) %>% {
      . * 100
    }
  
  # calculate similarity
  if (similarity == "BR") {
    g = dist(m, 'manhattan') %>%
      as.matrix
    g = 1 - (g / 200)
    diag(g) = 0
    g[] = round(g, 2)
  } else {
    g = weightedJaccard(m)
    g[] = round(g, 2)
  }
  
  links = g %>%
    as.data.frame() %>%
    rownames_to_column('from') %>%
    pivot_longer(-from, names_to = 'to',
                 values_to = 'weight') %>%
    # remove duplicate links
    dplyr::rowwise() %>%
    mutate(combo = paste(min(from, to), max(from, to))) %>%
    arrange(desc(to)) %>%
    distinct(combo, .keep_all = T) %>%
    select(-combo)
  cutoff = quantile(links$weight, cutoff)
  links %<>%
    filter(weight > 0, weight >= cutoff)
  if (group != "band" & 'band' %in% names(analysis)) {
    nodes = links %>%
      select(from, to) %>%
      pivot_longer(c(from, to), values_to = "name", names_to = 'var') %>%
      select(name) %>%
      arrange(name) %>%
      distinct_all() %>%
      left_join(analysis %>%
                  select(name = site, band) %>%
                  mutate_at(vars(name), as.character),
                by = "name") %>%
      mutate(camp = name) %>%
      distinct_all() %>%
      mutate_at(vars(band), factor)
  } else
    nodes = analysis %>% 
    ungroup() %>% 
    select(any_of(group)) %>% 
    mutate(name = !!as.name(group)) %>% 
    distinct_all()
  
  return(list(links = links, nodes = nodes))
}

#' Calculate weighted Jaccard 
weightedJaccard = function(m) {
  #' weighted jaccard similarity matrix setup
  #' from:
  #' https://rpubs.com/lgadar/weighted-jaccard
  
  r = matrix(0, nrow = nrow(m), ncol = nrow(m))
  rownames(r) = rownames(m)
  colnames(r) = rownames(m)
  
  #weighted jaccard
  pairs = t(combn(1:nrow(m), 2))
  for (i in 1:nrow(pairs)) {
    num =
      sum(sapply(1:ncol(m), function(x)
        (min(m[pairs[i, 1], x], m[pairs[i, 2], x]))))
    den =
      sum(sapply(1:ncol(m), function(x)
        (max(m[pairs[i, 1], x], m[pairs[i, 2], x]))))
    r[pairs[i, 1], pairs[i, 2]] = num / den
    r[pairs[i, 2], pairs[i, 1]] = num / den
  }
  r[which(is.na(r))] = 0
  diag(r) = 0
  return(r)
}

#' Select a proportion of the data either randomly or nonrandomly
sampleData = function(df,
                      p, # proportion of each site to keep
                      method # c("random","nonrandom")
){
  s = df %>%
    group_by(site) %>%
    count() %>%
    mutate(c = floor(n * p),
           c = case_when(c == 0 ~ 1, TRUE ~ c))
  if (method == "random") {
    rs = df %>%
      group_by(site) %>%
      group_split()
    r = map2_dfr(rs, s$c,  ~ {
      .x %>%
        slice_sample(n = .y)
    })
  } else {
    rs = df %>%
      slice(gtools::mixedorder(site)) %>%
      arrange(site) %>%
      rowid_to_column() %>%
      group_by(site) %>%
      group_split()
    r = map2_dfr(rs,
                 s$c, function(rsi, si) {
                   print('asdf')
                   indx = rsi %>%
                     group_by(site) %>%
                     slice_sample(n = 1) %>%
                     pull(rowid)
                   
                   indx2 = indx + si
                   if (indx2 > max(rsi$rowid)) {
                     tmp1 = rsi %>%
                       filter(rowid >= indx,
                              rowid <= max(rsi$rowid))
                     n = si - nrow(tmp1)
                     indx = rsi$rowid[which.min(rsi$rowid)]
                     indx2 = indx + n
                     
                     tmp2 = rsi %>%
                       filter(rowid >= indx,
                              rowid < indx2)
                     rsi = bind_rows(tmp1, tmp2)
                   } else {
                     rsi %<>%
                       filter(rowid >= indx,
                              rowid < indx2)
                   }
                   return(rsi)
                 })
  }
  return(r)
}
```

## Load data and set parameters

```{r}
# set seed for reproducibility
set.seed(1010)

# load ArchMatNet output
run = "15-Oct-2021-010258.048PM.csv"

# load ArchMatNet results
runResults = loadRun(run)

# variable to control whether files are saved
save = F
```

# Material and interaction networks

## Examine data

```{r}
# modify data
analysis = formatAssemblages(runResults$assemblages)

#' view tables of counts by type, band,
#' camp (site), and interaction type
table(analysis$tool,analysis$type)
table(analysis$band,analysis$type)
table(analysis$site,analysis$type)
runResults$links %>% 
  select(-end1,-end2) %>% 
  summarize_all(sum)
```

## Individual Attribute Networks

```{r}
g1 = attrNetworks(runResults,
                  attr = "potAttributes",
                  group = "who")

g2 = attrNetworks(runResults,
                  attr = "pointAttributes",
                  group = "who")

groups = c("pot","point")
links = bind_rows(g1$links %>% 
                    mutate(group = groups[1]),
                  g2$links %>% 
                    mutate(group = groups[2]))
n = igraph::graph_from_data_frame(links, directed = F)
plotdf = ggnetwork::ggnetwork(n) %>%
  as_tibble %>%  
  mutate(weight = weight %>% as.numeric) %>%
  left_join(bind_rows(g1$nodes,g2$nodes) %>% mutate_at(vars(name), as.character),
            by = "name")
plotdf %<>% 
  filter(!is.na(group)) %>% 
  bind_rows(
    map_dfr(groups,function(g){
      plotdf %>% filter(is.na(group)) %>% 
        mutate(group = g)
    })
  ) %>% 
  mutate(group = factor(group, levels = groups))
f1 = guide_legend(
  override.aes = list(shape = 21),
  ncol = 2,
  direction = "vertical"
)

plotdf %>%
  ggplot(aes(
    x = x,
    y = y,
    xend = xend,
    yend = yend
  )) +
  geom_edges(aes(color = group), size = .75) +
  geom_point(aes(shape = band,
                 fill = camp),
             size = 8) +
  scale_fill_brewer(palette = 'Set1') +
  scale_shape_manual(values = c(21,22,24)) +
  theme_blank() +
  theme(legend.position = "left",
        legend.background = element_rect(fill = F),
        strip.background = element_rect(
          color="white", fill="white", size=0, linetype="solid"
        ),
        strip.text = element_text(size = 12,hjust = 0)) +
  guides(fill = f1)

if(save == T){
  ggsave(
    "plots/Figure3.eps",
    width = 16,
    height = 20,
    units = "cm",
    device = cairo_ps
  )
  ggsave(
    "plots/Figure3.jpg",
    width = 16,
    height = 20,
    units = "cm",
    dpi = 450
  )
}
```

## Adjacency table networks

```{r fig.height=10, fig.width=7}
# ArchMatNet has reporters to output adjacency tables while running experiments. Because individuals can move to new camps, interactions have to be tracked directly between camps, as well as individuals. This example output provides a more accurate view of interactions between camps  
runs = read_csv(
  "results/ArchMatNetExperimentOutput.csv",
  skip = 6) %>% 
  janitor::clean_names()
nB = runs$n_of_bands %>% unique
nms = names(runs) %>% 
  str_remove_all("word_matrix_to_row_list_camp_")
names(runs) = nms
results = runs %>% 
  pivot_longer(c(trading_adjacency,
                 visiting_adjacency,
                 hunting_adjacency,
                 learning_adjacency,
                 point_adjacency,
                 pot_adjacency), names_to = "property",
               values_to = "adj") %>% 
  unite('id', run_number, property, remove = F)

adjTables = map2(results$adj,results$id,
                 formatNLAdjTables, nB = nB, cutoff = 0) %>% 
  setNames(results$id)

# scaling function
scale_this = function(x) as.vector(scale(x))

links = bind_rows(
  adjTables$`1_trading_adjacency`$links,
  adjTables$`1_visiting_adjacency`$links,
  adjTables$`1_hunting_adjacency`$links,
  adjTables$`1_learning_adjacency`$links
) %>% 
  group_by(property) %>% 
  mutate(weight = scale_this(weight)) %>% 
  ungroup()
n = igraph::graph_from_data_frame(adjTables$`1_trading_adjacency`$links,
                                  directed = F)
layout = igraph::layout.auto(n) %>%
  as.data.frame() %>%
  setNames(c("x", "y")) %>%
  mutate(name =  V(n)$name) %>%
  slice(gtools::mixedorder(name))

nodes = adjTables$`1_trading_adjacency`$nodes

groups = c("visiting", "hunting", "trading", "learning")

plotdf = links %>%
  rename(name = from) %>%
  full_join(layout, by = "name") %>%
  left_join(layout %>% rename(
    to = name,
    xend = x,
    yend = y
  ),
  by = "to") %>%
  as_tibble %>%  
  filter(!is.na(property)) %>% 
  bind_rows(
    map_dfr(groups,function(g){
      layout %>% 
        mutate(property = g)
    })
  ) %>% 
  mutate(property = factor(property, levels = groups)) %>% 
  mutate(weight = weight %>% as.numeric) %>%
  left_join(nodes %>% mutate_at(vars(name), as.character),
            by = "name") %>% 
  distinct_all()

plotdf %>%
  ggplot(aes(
    x = x,
    y = y,
    xend = xend,
    yend = yend
  )) +
  geom_edges(aes(color = weight), size = .75) +
  geom_point(aes(shape = band),
             size = 7) +
  scale_shape_manual(values = c(15,17,19)) +
  scale_color_viridis_c(direction = -1,
                        breaks = c(min(plotdf$weight, na.rm = T),
                                   max(plotdf$weight, na.rm = T)),
                        labels = c("low", "high")
  ) +
  geom_nodetext(
    aes(label = name),
    fontface = 'bold',
    color = 'white'
  ) +
  theme_blank() +
  theme(legend.position = "bottom",
        legend.background = element_rect(fill = F),
        strip.background = element_rect(
          color="white", fill="white", size=0, linetype="solid"
        ),
        strip.text = element_text(size = 12,hjust = 0)) +
  guides(
    shape = guide_legend(direction = "horizontal"),
    color = guide_colorbar(direction = "horizontal")
  ) +
  facet_wrap(~property, ncol = 2) +
  scale_y_continuous(expand = expansion(mult = .1)) +
  scale_x_continuous(expand = expansion(mult = .1))

if(save == T){
  ggsave(
    "plots/Figure4.eps",
    width = 16,
    height = 20,
    units = "cm",
    device = cairo_ps
  )
  ggsave(
    "plots/Figure4.jpg",
    width = 16,
    height = 20,
    units = "cm",
    dpi = 450
  )
}
```


# Sampling bias ArchMatNet


## Calculate weighted Jaccard distances for total dataset and 20% samples

```{r}
analysis = formatAssemblages(runResults$assemblages) %>% 
  filter(type == "pot")

g1 = calcDistanceTools(analysis,
                        toolType = "pot",
                        group = 'site',
                        cutoff = 0.5,
                        similarity = "WJ")

sample1 = sampleData(analysis,.2,"random")
g2 = calcDistanceTools(sample1,
                        toolType = "pot",
                        group = 'site',
                        cutoff = 0.5,
                        similarity = "WJ")

sample2 = sampleData(df = analysis,p = .2,method = "nonrandom")
g3 = calcDistanceTools(sample2,
                        toolType = "pot",
                        group = 'site',
                        cutoff = 0.5,
                        similarity = "WJ")
```

## Combine and plot results

```{r fig.height=10, fig.width=7}
groups = c("all","random sample","nonrandom sample")
links = bind_rows(g1$links %>% 
                    mutate(group = groups[1]),
                  g2$links %>% 
                    mutate(group = groups[2]),
                  g3$links %>% 
                    mutate(group = groups[3]))

n = igraph::graph_from_data_frame(links, directed = F)
plotdf = ggnetwork::ggnetwork(n) %>%
  as_tibble %>%  
  mutate(weight = weight %>% as.numeric) %>%
  left_join(g1$nodes %>% mutate_at(vars(name), as.character),
            by = "name")
plotdf %<>% 
  filter(!is.na(group)) %>% 
  bind_rows(
    map_dfr(groups,function(g){
      plotdf %>% filter(is.na(group)) %>% 
        mutate(group = g)
    })
  ) %>% 
  mutate(group = factor(group, levels = groups))

plotdf %>%
  ggplot(aes(
    x = x,
    y = y,
    xend = xend,
    yend = yend
  )) +
  geom_edges(aes(color = weight), size = .75) +
  geom_point(aes(shape = band),
             size = 10) +
  scale_shape_manual(values = c(15,17,19)) +
  scale_color_viridis_c(direction = -1) +
  geom_nodetext(
    aes(label = name),
    fontface = 'bold',
    color = 'white'
  ) +
  theme_blank() +
  theme(legend.position = "bottom",
        legend.background = element_rect(fill = F),
        strip.background = element_rect(
          color="white", fill="white", size=0, linetype="solid"
        ),
        strip.text = element_text(size = 12,hjust = 0)) +
  guides(
    shape = guide_legend(direction = "horizontal"),
    color = guide_colorbar(direction = "horizontal")
  ) +
  facet_wrap(~group, ncol = 1)

if(save == T){
  ggsave(
    "plots/Figure6.eps",
    width = 16,
    height = 27.4,
    units = "cm",
    device = cairo_ps
  )
  
  ggsave(
    "plots/Figure6.jpg",
    width = 16,
    height = 27.4,
    units = "cm",
    dpi = 450
  )
}
```

## Take 1000 random samples for each proportion size

Note: commented out due to length of time to calculate--saved data used instead

```{r}
# library(tictoc)
# library(furrr)
# tic()
# future::plan('multisession')
# 
# random = 
#   future_map_dfr(1:1000,~
#                    compareMissing(df = analysis,
#                                   group = 'tick',
#                                   prop = seq(.001,1,.1),
#                                   method = "random"),.progress = T)
# saveRDS(random,'results/randomSamples.Rds')
# 
# nonrandom = 
#   future_map_dfr(
#     1:1000,~
#       compareMissing(df = analysis,
#                      group = 'tick',
#                      prop = seq(.001,1,.1),
#                      method = "nonrandom"),.progress = T)
# saveRDS(nonrandom,'results/nonrandomSamples.Rds')
# toc()

# load and combine data
random = readRDS('results/randomSamples.Rds')
nonrandom = readRDS('results/nonrandomSamples.Rds')

simulated = bind_rows(random,nonrandom)%>% 
  mutate(proportion = sprintf("%1.1f%%", 100*proportion),
         method = factor(method, levels = c("random","nonrandom")))
```

## Compare results

```{r}
groups = simulated$proportion %>% unique

statResults = map_df(groups,function(g){
  x = simulated %>% 
    filter(method == "random", proportion == g) %>% 
    pull(distance)
  y = simulated %>% 
    filter(method == "nonrandom", proportion == g) %>% 
    pull(distance)
  c = simulated %>% 
    filter(method == "nonrandom", proportion == g) %>% 
    pull(count) %>% unique
  
  pVal = t.test(x,y,alternative = "less")
  tibble(`sample proportion` = g,
         `sample size` = c,
         `random mean` = mean(x),
         `nonrandom mean` = mean(y),
         pVal = pVal$p.value) %>% 
    mutate_at(vars(2:4),round, digits = 3)
}) %>% 
  mutate(`p-value` = case_when(pVal == 0 ~ "0",
                               pVal < .001 ~ "<0.001",
                               TRUE ~ as.character(pVal)))


h = statResults %>% select(-pVal) %>%
  as_hux() %>%
  set_number_format(everywhere, 2, huxtable::fmt_pretty()) %>% 
  huxtable::theme_article()
h
if(save == T){
  h %>% quick_docx(file = "tbls/Table1.docx")
  h %>% quick_xlsx(file = "tbls/Table1.xlsx")
}
```

## Plot results

```{r fig.height=5, fig.width=7}
simulated %>% 
  ggplot(aes(x = factor(proportion),y = distance,
             color = proportion)) + 
  geom_boxplot(notch = T) +
  theme_gdocs(base_family = "") +
  ylab("Laplacian distance") +
  xlab("sample size") +
  theme(axis.text = element_text(size = 9)) +
  guides(color = "none") + 
  facet_wrap(~method) +
  coord_flip()

if(save == T){
  ggsave("plots/Figure7.eps", width = 6.2, device = cairo_ps)
  ggsave("plots/Figure7.jpg", width = 6.2, dpi = 450)
}
```

# Sampling Bias Obsidian

## Load and view obsidian data

```{r}
obsidianData = readRDS("results/RPMSObsidian.Rds") %>% ungroup()
knitr::kable(
  table(obsidianData$ASM,obsidianData$SOURCE)
)
```

## Plot obsidian network

```{r fig.height=5, fig.width=7}
# bipartite network
bi = obsidianData %>% 
  select(source = SOURCE, site = ASM) %>% 
  distinct_all()
n = igraph::graph_from_data_frame(bi, directed = F)

nodes = bind_rows(bi %>% select(name = source) %>%
                    distinct_all() %>% 
                    mutate(type = "obsidian source"),
                  bi %>% select(name = site) %>%
                    distinct_all() %>% 
                    mutate(type = "site")
)
plotdf = ggnetwork(n) %>% 
  as_tibble() %>% 
  full_join(nodes)

plotdf %>%
  ggplot(aes(
    x = x,
    y = y,
    xend = xend,
    yend = yend
  )) +
  geom_edges(color = 'black',
             size = .5) +
  geom_point(aes(shape = type, color = type),
             size = 10) +
  scale_shape_manual(values = c(15, 17, 19))+
  geom_nodetext(aes(label = name), size = 3) +
  theme_blank() +
  theme(legend.position = "bottom",
        legend.background = element_rect(fill = F),
        legend.title = element_blank()) +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(expand = expansion(mult = .1)) +
  scale_x_continuous(expand = expansion(mult = .1))

if(save == T){
  ggsave("plots/Figure5.eps", width = 6.2, device = cairo_ps)
  ggsave("plots/Figure5.jpg", width = 6.2, dpi = 450)
}
```

## Create weighted Jaccard network

```{r}
analysis = obsidianData %>% select(tool = SOURCE,
                               site = ASM,
                               feature = FEATURE) %>% 
  mutate(type = "obsidian")



g1 = calcDistanceTools(analysis = analysis,
                       toolType = "obsidian",
                       group = 'site',
                       cutoff = .5)
```

## Plot weighted Jaccard network

```{r fig.height=5, fig.width=7}
n = igraph::graph_from_data_frame(g1$links, directed = F)
plotdf = ggnetwork::ggnetwork(n) %>%
  as_tibble

plotdf %<>%
  mutate(weight = weight %>% as.numeric) %>%
  left_join(nodes %>% mutate_at(vars(name), as.character),
            by = "name")

plotdf %>%
  ggplot(aes(
    x = x,
    y = y,
    xend = xend,
    yend = yend
  )) +
  geom_edges(aes(color = weight), size = .75) +
  scale_color_viridis_c(direction = -1,
                        breaks = c(min(plotdf$weight, na.rm = T),
                                   max(plotdf$weight, na.rm = T)),
                        labels = c("low", "high")
  ) +
  geom_point(size = 8,
             color = "black",
             shape = 19) +
  theme_blank() +
  theme(legend.position = "bottom",
        legend.background = element_rect(fill = F)) +
  guides(
    shape = guide_legend(direction = "horizontal"),
    color = guide_colorbar(direction = "horizontal",
                           title.position = "top")
  )

if(save == T){
  ggsave("plots/Figure8.eps", width = 6.2, device = cairo_ps)
  ggsave("plots/Figure8.jpg", width = 6.2, dpi = 450)
}
```

## Take 1000 random samples for each proportion size

Note: commented out due to length of time to calculate--saved data used instead

```{r}
# library(furrr)
# future::plan('multisession')
# randomObsidian = future_map_dfr(1:1000,~
#                                   compareMissing(df = analysis,
#                                                  group = 'feature',
#                                                  prop = seq(.25,.75,.25),
#                                                  method = "random"))
# saveRDS(randomObsidian,'results/randomObsidianSamples.Rds')

# nonrandomObsidian = future_map_dfr(
#   1:1000,~
#     compareMissing(df = analysis,
#                    group = 'feature',
#                    prop = seq(.25,.75,.25),
#                    method = "nonrandom"))
# saveRDS(nonrandomObsidian,'results/nonrandomObsidianSamples.Rds')

# load saved data
randomObsidian = readRDS('results/randomObsidianSamples.Rds')
nonrandomObsidian = readRDS('results/nonrandomObsidianSamples.Rds')
obsidian = bind_rows(random,nonrandom) %>% 
  filter(!is.na(distance),proportion != 1) %>% 
  mutate_at(vars(distance),list(~case_when(.x > 20~20,TRUE~.x))) %>% 
  mutate(proportion = sprintf("%1.1f%%", 100*proportion),
         method = factor(method, levels = c("random","nonrandom")))
```

## Compare results

```{r}
groups = obsidian$proportion %>% unique

statResults = map_df(groups,function(g){
  x = obsidian %>% 
    filter(method == "random", proportion == g) %>% 
    pull(distance)
  y = obsidian %>% 
    filter(method == "nonrandom", proportion == g) %>% 
    pull(distance)
  # note -- samplifying function introduced some variation in the sample size
  # most common value for each sample proportion is reported
  c = obsidian %>% 
    filter(method == "nonrandom", proportion == g) %>% 
    pull(count) %>% unique %>% median() %>% as.integer
  
  pVal = t.test(x,y,alternative = "less")
  tibble(`sample proportion` = g,
         `sample size` = c,
         `random mean` = mean(x),
         `nonrandom mean` = mean(y),
         pVal = pVal$p.value) %>% 
    mutate_at(vars(2:5),round, digits = 3)
}) %>% 
  mutate(`p-value` = case_when(pVal == 0 ~ "0",
                               pVal < .001 ~ "<0.001",
                               TRUE ~ as.character(pVal))) %>% 
  slice(c(1,3,2))

h = statResults %>% select(-pVal) %>% as_hux() %>% huxtable::theme_article()
h
if(save == T){
  h %>% quick_docx(file = "tbls/Table2.docx")
  h %>% quick_xlsx(file = "tbls/Table2.xlsx")
}
```

## Plot results

```{r fig.height=5, fig.width=7}
# plot
obsidian %>% 
  ggplot(aes(x = factor(proportion),y = distance, color = proportion)) + 
  geom_boxplot(notch = T) +
  theme_gdocs(base_family = "") +
  ylab("Laplacian distance") +
  xlab("sample size") +
  theme(axis.text = element_text(size = 9)) +
  guides(color = "none") + 
  facet_wrap(~method) +
  coord_flip()

if(save == T){
  ggsave("plots/Figure9.eps", width = 6.2, device = cairo_ps)
  ggsave("plots/Figure9.jpg", width = 6.2, dpi = 450)
}
```

# System Information

```{r}
sessionInfo()
```

